Bulk Semantic Annotation with a Partially Known Knowledge Base

### 2024-12-04 doc/cicm25-sysdesc/sysdesc.tex
drain

The \snify system (see \cite{stextools:git}) is a simple command-line tool.
It creates a database of symbol-verbalization pairs, analyzes \sTeX source files,
and then steps through all word occurrences in the document that match a
verbalization in the database.
Matching is based on word stems using off-the-shelf stemmers, which allows us to
e.g.\ match ``utilities'' with ``utility''.
For each matched word, the user is presented with an annotation choice and
interactions that allow to fine-tune the wordwise annotation workflow. \Cref{fig:snify}
shows a typical situation.

>>>>

The \snify\ednote{explain name? write as sn-ify?}
system (see \cite{stextools:git}) is a simple command-line tool
that creates a database of symbol-verbalization pairs, analyzes \sTeX source files,
and then steps through all word occurrences in the document that match a
verbalization in the database.
Matching is based on word stems using off-the-shelf stemmers, which allows us to
e.g.\ match ``utilities'' with ``utility''.
For each matched word, the user is presented with an annotation choice and
interactions that allow to fine-tune the wordwise annotation workflow. \Cref{fig:snify}
shows a typical situation.
